NSAIDs

### 2021-01-22 r_notebooks/preparing_nsaid.Rmd
Typos

nsaid <- 
  read_rds("../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

>>>>

nsaid <- 
  read_rds("../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))
